---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# canbank

<!-- badges: start -->
[![R-CMD-check](https://github.com/mountainMath/canbank/workflows/R-CMD-check/badge.svg)](https://github.com/mountainMath/canbank/actions)
<!-- badges: end -->

<a href="https://mountainmath.github.io/canbank/index.html"><img src="https://mountainmath.github.io/canbank/logo.svg" alt="canbank logo" align="right" width = "25%" height = "25%"/></a>

An R package to provide convenient access to the Bank of Canada data API.

# Documentation
[canbank R package home page and reference guide](https://mountainmath.github.io/canbank/index.html)


## Installation

You can install the released version of canbank from [CRAN](https://CRAN.R-project.org) with:

``` r
remotes::install_github("mountainmath/canbank")
```

## Example

The package can import data for one or several Bank of Canada time series or series groups. For example, to access the series group "SAN_MIKA20210428_C1" with metrics pertaining to house price growth in Canada we can easily retrieve the data using the `get_boc_series_group` method.

```{r example, message=FALSE, warning=FALSE}
library(canbank)
library(dplyr)
library(ggplot2)
## basic example code

data <- get_boc_series_group("SAN_MIKA20210428_C1") %>%
  mutate(name=gsub(" \\(.+$","",label)) %>%
  filter(!is.na(Value))

ggplot(data,aes(x=Date,y=Value)) +
  geom_line() +
  facet_wrap(~name, scales="free") +
  labs(title="House price metrics",
       y=NULL,x=NULL,
       caption="Bank of Canada series group SAN_MIKA20210428_C1")
```

