---
title: "Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dplyr)
library(ggplot2)
library(canbank)
```

The package gives access ot the Bank of Canada data API. Currently there are `r scales::comma(nrow(list_boc_series()))` data series available, grouped into `r scales::comma(nrow(list_boc_series_groups()))`. We obtain basic information for the series or series groups.

```{r}
series_list <- list_boc_series()
series_group_list <- list_boc_series_groups()

head(series_list) %>% knitr::kable()
```



Data discovery is still somewhat cumbersome, we can search for phrases in the labels or description.

```{r}
series_list %>%
  filter(grepl("home",label,ignore.case = TRUE)) %>% 
  select(-link) %>%
  knitr::kable()
```


If we are intersted in MLS home price index, we might want to inspect the series group FSHUB_20210317_C2.

```{r}
get_boc_series_group("FSHUB_20210317_C2") %>%
  mutate(name=gsub(" \\(.+\\)$","",label)) %>%
  ggplot(aes(x=date,y=value)) +
  geom_line(colour="steelblue",size=1) +
  geom_smooth(se=FALSE,method="lm",formula=y~1,colour="brown",size=0.5) +
  facet_wrap(~name,scales="free_y",ncol=1) +
  labs(title="MLS overview data for Canada with long-run averages",
       x=NULL,y=NULL,
       caption="Source: Bank of Canada series group FSHUB_20210317_C2")
```







